---
title: "Equine Saddle Pressure Analysis with pressR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Equine Saddle Pressure Analysis with pressR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<!-- badges: start -->
[![R-CMD-check](https://github.com/CTTIR/pressR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CTTIR/pressR/actions/workflows/R-CMD-check.yaml)
[![pkgdown](https://github.com/CTTIR/pressR/actions/workflows/pkgdown.yaml/badge.svg)](https://cttir.github.io/pressR/)
[![CRAN status](https://www.r-pkg.org/badges/version/pressR)](https://CRAN.R-project.org/package=pressR)
[![Codecov test coverage](https://codecov.io/gh/CTTIR/pressR/branch/main/graph/badge.svg)](https://app.codecov.io/gh/CTTIR/pressR?branch=main)
[![CRAN downloads](https://cranlogs.r-pkg.org/badges/pressR)](https://cran.r-project.org/package=pressR)
[![CRAN downloads total](https://cranlogs.r-pkg.org/badges/grand-total/pressR)](https://cran.r-project.org/package=pressR)
[![License: MIT](https://img.shields.io/badge/license-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>",
  fig.width = 7, fig.height = 5, dpi = 96
)
```

```{r setup, message=FALSE}
library(pressR)
```

Saddle-pressure mapping using capacitive sensor mats has been used
extensively in the equine back-health literature (Werner et al. 2002;
Moenkemoeller et al. 2005; von Peinen et al. 2010). This vignette
walks through a typical analysis.

## Load the saddle layout

```{r}
layout <- pr_layout_saddle("horse")
names(layout$regions)
```

## Load a synthetic trial

```{r}
trial <- pr_example_trial("saddle_horse")
trial
```

## Inspect the pressure map

```{r, fig.alt="Saddle pressure heatmap with 6-region mask"}
pr_plot_heatmap_masked(trial)
```

## Regional analysis with reference thresholds

```{r}
masks <- pr_mask_saddle_6(layout)
reg <- pr_calc_regional(trial, masks)
reg
```

```{r, fig.alt="Regional mean-pressure bar chart"}
pr_plot_regional_bar(reg, "mvp", thresholds = pr_ref_saddle())
```

## Bridge detection

```{r}
bridge <- pr_calc_saddle_bridge(trial)
bridge
```

## Slip / asymmetric loading

```{r}
slip <- pr_calc_saddle_slip(trial)
slip$symmetry_index_mean
slip$dominant_side
```

## Composite report

```{r, fig.alt="Saddle-fit composite report", fig.width=9, fig.height=7}
pr_plot_saddle_report(trial)
```

## References

* Werner D, et al. (2002). *J Vet Med A Physiol Pathol Clin Med* 49(9): 460-465.
* Moenkemoeller S, et al. (2005). *Pferdeheilkunde* 21(2): 102-108.
* von Peinen K, et al. (2010). *Equine Vet J Suppl* 42: 650-653.
